---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# spfa

<!-- badges: start -->
<!-- badges: end -->

The package provides estimation, scoring, and plotting functions for the semiparametric parametric factor model proposed by Liu & Wang (2022; 2023). Both the conditional densities of observed responses given the latent factors and the joint density of latent factors are estimated nonparametrically. Functional parameters are approximated by smoothing splines, whose coefficients are estimated by penalized maximum likehood using an expectation-maximization (EM) algorithm. E- and M-steps can be parallelized on multi-thread computing platforms that support OpenMP. Both continuous and unordered categorical response variables are supported.


## Installation

You can install the development version of spfa from [GitHub](https://github.com/), with:

``` r
# install.packages("devtools")
devtools::install_github("wwang1370/spfa")
```

## Example

Various examples and worked help files have been compiled using the knitr package to generate HTML output, and are available on the package help file. User contributions are welcome!

```{r example}
library(spfa)
## basic example code includes fitting an spfa model for response time
#  RT <- spfa::simdata[,1:8]
# spfa_example <- spfa(data = RT, 
#       dimension = rep(0, ncol(RT)), 
#       discrete = rep(F, ncol(RT)))
```
## citation:

Liu, Y., & Wang, W. (2022). Semiparametric factor analysis for item-level response time data. Psychometrika, 87(2), 666-692.
Liu, Y., & Wang, W. (2023). What Can We Learn from a Semiparametric Factor Analysis of Item Responses and Response Time? An Illustration with the PISA 2015 Data. Retrieved from \url{http://arxiv.org/abs/2303.10079}


